Fourmile state variables

### 2025-03-18 state_vars.Rmd
created figure for high and low HRU - tmean & SWE

library(tidyverse)
library(ggplot2); theme_set(theme_bw(base_size = 20))
library(plotly)
library(knitr)
library(kableExtra)

@@

statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_19.csv') %>% 
  mutate(date = mdy(time),
         source = 'statn') %>%
  dplyr::select(-time)

grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_19.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  dplyr::select(-time)

@@

@@

>>>>

library(tidyverse)
library(ggplot2); theme_set(theme_bw(base_size = 20))
library(plotly)
library(knitr)
library(kableExtra)
library(cowplot)

@@

statn_low <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_19.csv') %>% 
  mutate(date = mdy(time),
         source = 'statn') %>%
  dplyr::select(-time)

grid_low <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_19.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  dplyr::select(-time)

both_low <- bind_rows(statn_low, grid_low) %>%
  mutate(year = year(date),
         month = month(date)) %>%
  filter(year == 2015,
         month %in% c(4,5,6))

temp <- ggplot(both_low, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

swe <- ggplot(both_low, 
               aes(date, 
                   snowTotSWE,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

## combine low and high together
hi <- both_hi %>%
  dplyr::select(tmean, snowTotSWE, source, date) %>%
  mutate(elevation = 'High')

low <- both_low %>%
  dplyr::select(tmean, snowTotSWE, source, date) %>%
  mutate(elevation = 'Low')

both <- bind_rows(hi, low) %>%
  mutate(elev_source =
           case_when(source == 'statn' & elevation == 'High' ~ 'Station - High',
                     source == 'statn' & elevation == 'Low' ~ 'Station - Low',
                     source == 'grid' & elevation == 'High' ~ 'Gridded - High',
                     source == 'grid' & elevation == 'Low' ~ 'Gridded - Low'))

# figure
tmean <- ggplot(both,
       aes(x=date, y = tmean, 
           color = elev_source,
           linetype=elev_source)) +
   geom_line(size=1, alpha=0.8) +  
    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
                                  "Gridded - Low" = "#0047AB", 
                                  "Station - High" = "orange",
                                  "Station - Low" = "orange")) +
  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
                                  "Gridded - Low" = "solid", 
                                  "Station - High" = "dashed",
                                  "Station - Low" = "solid")) + 
  scale_x_date(date_labels = "%b") +
  labs(x = element_blank(),
       y = 'Mean temperature (°C)') +
  theme_bw(base_size = 20) +
  theme(legend.position = "none",
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    legend.key.width = unit(1, "cm")
    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
  )

swe <- ggplot(both,
       aes(x=date, y = snowTotSWE, 
           color = elev_source,
           linetype=elev_source)) +
   geom_line(size=1, alpha=0.8) +  
    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
                                  "Gridded - Low" = "#0047AB", 
                                  "Station - High" = "orange",
                                  "Station - Low" = "orange")) +
  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
                                  "Gridded - Low" = "solid", 
                                  "Station - High" = "dashed",
                                  "Station - Low" = "solid")) + 
  scale_x_date(date_labels = "%b") +
  #scale_y_log10() +
  labs(x = element_blank(),
       y = 'SWE (mm)') +
  theme_bw(base_size = 20) +
  theme(
    legend.position = c(0.74, 0.85),
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    legend.key.width = unit(1, "cm")
    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
  )

swe

plot_grid(tmean, swe)

ggsave('./figures/tmean_swe_2015.png',
       width = 10,
       height = 5,
       dpi=600)
